---
output:
  pagedown::html_paged:
    css: ["css/one-column-paged-academic.css",  "https://use.fontawesome.com/releases/v5.7.2/css/all.css"]
    number_sections: false
links-to-footnotes: true
knit: pagedown::chrome_print
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(lubridate)
library(glue)

######## CREATE HELPER FUNCTIONS
# function which takes a name and replaces the first name with initial and dot
replace_first_name_with_initial_and_dot <- function(author_name) {
  str_replace(author_name, "(?<=\\S)\\S+", "\\.")
}

# function for doing this for an entry with a number of authors
replace_first_names_in_list_with_initial_and_dot <- function(authors){
  authors_split <- str_split(authors, ",") %>% 
    map(str_trim)
  
  authors_split[[1]] %>% map_chr(replace_first_name_with_initial_and_dot) %>% 
    paste0(collapse = ", ")
}

# function for adding leading zero's when there's more than 10 entries
padding_function <- function(cv_entries_tibble, letter_to_pad){
  if(nrow(cv_entries_tibble) > 9){
    cv_entries_tibble %>% 
      arrange(date) %>%
  mutate(number = str_pad(row_number(), width = 2, side = "left", pad = "0"),
         number = str_c(letter_to_pad, number)) %>%
  arrange(desc(date))
  } else {
    cv_entries_tibble %>% 
      arrange(date) %>%
  mutate(number = str_pad(row_number(), width = 1, side = "left", pad = "0"),
         number = str_c(letter_to_pad, number)) %>%
  arrange(desc(date))
  }
}

# function for making a year blank when it's the same as the one preceding it
blank_year_when_repeated <- function(cv_entry_tibble){
  cv_entry_tibble %>% 
    mutate(row_number = row_number()) %>% 
    mutate(year = as.character(year),
           year = case_when(
             row_number == 1 ~ year,
             year == lag(year) ~ "",
             year != lag(year) ~ year
           )) %>% 
    select(-row_number)
}


####### READ IN DATA
#### publications #####
publications <- read_csv("_content/publications.csv") %>% 
  mutate(authors_full = map_chr(authors_full, replace_first_names_in_list_with_initial_and_dot)) %>% 
  mutate(authors_full = str_replace(authors_full, "U\\. Lyngs", "*U\\. Lyngs*")) %>%    # make my name italic
  mutate(year = year(date)) %>% 
  mutate(venue_abbrev = if_else(!is.na(venue_abbrev), str_c(venue_abbrev, ": "), "")) # make the abbrevation an empty string if NA; add a colon and a space after if it if there is one

#### cv entries #####
cv_entries <- read_csv("_content/cv_entries.csv") %>% 
  mutate(year = year(date)) %>%
  mutate(year_end = case_when(
    date_end == "present" ~ date_end,
    !is.na(date_end) ~ str_sub(date_end, 1, 4),
    is.na(date_end) ~ date_end
  )) %>%
  mutate(year = ifelse((is.na(year_end) | year == year_end),
                      year,
                      str_c(year, " --- ", year_end)))

```


```{css}
:root{
  --last-updated: "";
}
```


:::::: {.title-and-contact}

::: {.title}
<h1 class="title">Ásgeir Berg Matthíasson</h1>
:::

::: {.contact-info}
<br><br>
asgeirberg@hi.is  \
https://asgeirberg.com
:::

::::::

## Research interests
:::::: {.research-interests}

::: {.spacer}
:::

::: {.interests}

My current research project, which is funded by the *Icelandic Research Fund* (RANNÍS), is to develop a conventionalist account of mathematical truth, based on my previous work on the rule-following paradox and Wittgenstein's philosophy of mathematics.

**Areas of Specialisation:** Wittgenstein, philosophy of mathematics, philosophy of logic, the rule-following paradox.
<br>
<br>
**Areas of Competence:** Metaphysics, logic, epistemology,
history of analytic philosophy.

:::
::::::

<div class="cv-entries">
## Current position
```{r}
cv_entries %>% 
  filter(type == 'current', is.na(exclude)) %>%
  mutate(what = glue("<span class='cv-entry-title'>{what}</span><br>",
                     "{where}"
                     )) %>% 
  select(year, what) %>% 
  kable()
```

## Previous positions
```{r}
cv_entries %>% 
  filter(type == 'research_positions', is.na(exclude)) %>%
  mutate(what = glue("<span class='cv-entry-title'>{what}</span><br>",
                     "{where}"
                     )) %>% 
  select(year, what) %>% 
  kable()
```

## Education
```{r}
cv_entries %>% 
  filter(type == 'education') %>% 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}<br style='line-height:130%;'>", #widens the gap between the elements a bit.
                      "{additional_info}<br>",
                      "<span class='thesis-title'>{additional_info2}</span>")) %>% 
  select(year, what) %>% 
  kable()
```

## Publications {.three-split}

<h3>Journal articles</h3>

```{r}
publications %>%
  filter(type == "journal article") %>% 
  mutate(citation = glue("<span class='cv-entry-title'>{title}</span><br>",
                         "<span class='publication-venue'>{venue_abbrev}<i>{venue}</i></span>")) %>% 
  padding_function(., "J") %>% 
  blank_year_when_repeated() %>%
  select(year, number, citation) %>%
  knitr::kable()
```

## Selected talks {.three-split}

```{r}
cv_entries %>% 
  filter(type == 'talk', is.na(exclude)) %>% 
  # add commas as appropriate
  mutate(where = if_else(!is.na(where) & !is.na(institution), glue("{where}"), where),
         department = if_else(!is.na(department), glue(", {department}"), department),
         slides = if_else(!is.na(slides), glue("<a href={slides}>Slides</a>"), ""),
         video = if_else(!is.na(video), glue("<a href={video}>Video</a>"), "")) %>%
  mutate(additional_info = if_else(!is.na(additional_info), glue(", {additional_info}"), "")) %>% 
  mutate(what_translation = ifelse(!is.na(what_translation), str_c("(", what_translation, ")"), what_translation)) %>% 
  replace_na(list(what_translation = "")) %>% 
  mutate(what = glue("<span style='display:inline-block;' class='talk-title'>{what}</span>,<br style='line-height:130%;'>",
  					  "<span class='cv-entry-title'>{where}, {institution}</span><b>{department}{additional_info}</b><br>", 
                     .na = "")) %>% 
  padding_function(., "T") %>% 
  blank_year_when_repeated() %>% 
  select(year, number, what) %>% 
  knitr::kable()


```

## Grants, Awards and Fellowships
```{r}
cv_entries %>% 
  filter(type == 'awards') %>% 
  mutate(what = glue("<span class='cv-entry-award'>{what}</span>")) %>%  
  blank_year_when_repeated() %>% 
  select(year, what) %>% 
  kable()
```

## Reviewing and refereeing
```{r}
cv_entries %>% 
  filter(type == 'reviewing') %>% 
  mutate(what = glue("<span class='cv-entry-review'>{what}</span>",)) %>% 
   mutate(year = glue('')) %>% 
  select(year,what) %>% 
  kable()
```

<!-- close 'cv-entries' div -->
</div>

<br class="pageBreak">